\mytitile\\~

### 2020-05-12 PRA_referee_response.tex

	\item \textbf{Feature I in Fig2d (right hand side) clearly shows an anti-crossing
		(also the lines which according to the legend represent the
		unperturbed Hamiltonian) but later on it is said that feature I does
		not show an avoided level crossing if either the drives are the same
		or the Hamiltonian is unperturbed. Maybe the authors could clarify
		this.}

	We apologize again for this ambiguity. We name as feature I the apparent splitting of the transition 11/2 and the deviation of its frequency from the unperturbed Hamiltonian prediction while the avoided crossing 01 vs 10 is vanished and already not visible at such power. Looking closely at the color data in Fig. 2d of our paper, especially left hand side, one can not 
	resolve an anticrossing formed by the lines 01, 10 drawn as the model lines in the right. The only effect that is seen is that 11/2 is being bent and split, and that's exactly what we are interested in. So the problem is that we did not state explicitly the difference between feature I and the avoided crossing of 01, 10, and now we are doing that in the beginning of section III A.

	We will change the wording considering feature I. We will now call it a ``splitting of the spectral line 11/2'' to avoid confusion with the effect well studied in Filipp2011.

	``but later on it is said that feature I does
	not show an avoided level crossing if either the drives are the same
	or the Hamiltonian is unperturbed''

	We couldn't find the exact quote in our paper, but we can clarify this: yes, the splitting of 11/2 is not observed when the drive is symmetric, though from Fig. 4 of our paper we can see that its frequency is somewhat shifted upwards (we could not explain that). And if the Hamiltonian is unperturbed (no driving), then we only have the eigenlevels which of course yield continuous 11/2 line, as shown in Fig. 2 d of our paper. Additionally, if the Hamiltonian has no coupling term, 11/2 will not be visible, so feature I will not be present as well.

	\item \textbf{The discussion of feature I seems also to be inconsistent with what
		has already been observed in Filipp2011 where the qubits were driven
		via the resonator with approximately equal strength. Maybe the authors
		could clarify this point as well.}

	As I hope is clear from above, this is not the case, we just should have been more explicit in the paper stating the difference between feature I and the standard anticrossing located at the same point.

	\item \textbf{Specifically, why does the avoided crossing vanish for equal drive
		strength?}

	Talking about the feature I how we mean it (splitting of 11/2): this is explained it in the section III D, paragraph b, using Fig. 6 of our paper.

	The usual avoided crossing covered in Filipp2011 truly does not depend on the drive since it is not a consequence of light dressing, but one can't resolve it for our powers and linewidths in Fig. 4 of our paper.

	\item \textbf{Why is there no dark state (in feature I)?}

	We don't know why there are no selection rules in that case (how we mean it). But the numerical simulation supports that.

	Considering the usual avoided crossing, we have shown above that we can see it, and it is consistent with Filipp2011.

	\item \textbf{- the design looks beautiful and symmetric. Do the authors have a
	suspicion why the charge line couple twice as strong to one qubit than
	the other? Maybe there is a capacitive of even inductive interaction
	at play as well? If so, how would that modify the assumptions about
	the J coupling interaction?}

	Actually, the design is a bit asymmetric, as can be seen from Fig. 1a of our paper, the charge line goes closer to the higher frequency transmon (with larger Josephson junctions). Even though the line goes relatively far from it, and should have bean screened by airbridges, it still seems to couple stronger to the closer transmon. The coupling is still capacitive.

	We do not suspect inductive interaction since transmons are far less sensitive to that even for asymmetric SQUIDs (see the original paper, Koch2007), and we bring an open end of the line to the SAM, so the magnetic fields should be suppressed there.

	All that should not modify the assumptions about
	the $J$ coupling interaction because the resonator itself is symmetric, and we do not find any differences in the coupling capacitances to is both experimentally and from FEM modelling (see Appendix A.)

	\item \textbf{- at which flux/qubit frequencies were the T1 and T2 times extracted?
		Were they assumed to be frequency independent in the numerical model?}

	Yes, at the sweet spots, we mentioned that in the table. We assumed frequency-independent parameters in the model, which worked well enough because we have very strong driving and the linewidths are mostly larger than the dissipation rates.

	\item \textbf{- it is mentioned that the parameters changed due to a second
		cooldown. How and why did they change? What are the new values?}

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{Pictures/II-TTS}
		\caption{The spectrum of the SAM in the second cooldown.}
		\label{fig:ii-tts}
	\end{figure}

	This is a valid question, please find the new spectrum equivalent to Fig.2(a) of our paper in \autoref{fig:ii-tts}. The Josephson energies and sweet spot locations are shifting between cooldowns. While sweet spots can be readjusted, the frequency locations of the maxima and minima of the qubits can not, therefore we had a problem that feature III became too deformed with the new configuration of the transmon frequencies, and Feature I in now interfering with the spurious resonance.

	We chose not to reestimate the parameters for the numerical model because it is a cumbersome process and does not affect our final conclusions.

	\newpage

	\item \textbf{
		- it is mentioned that the change of the spectrum is of topological
		nature. What does that mean in this context?}

	We mean that the resulting configurations in Fig. 4 of our paper (row 1 vs. 2) can not be transformed into each other by a continuous deformation; this is because the lines that participate are different.

\end{enumerate}

\end{document}
